An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This work has been partially funded by CoMeDiC ANR-15-CE40-0006 research grant.}

### 2020-01-08 Revision/Biographies/biographies.tex
photos

\paragraph{Hugues Talbot}
Hugues Talbot received the Habilitation from Universite Paris-Est in 2013, the PhD from \'Ecole des Mines de Paris in
1993 and the engineering degree from Ecole Centrale de Paris in 1989. He was principal research scientist at CSIRO,
Sydney, from 1994 to 2004. He is now a professor at CentraleSupelec, Universite Paris-Saclay and member of the Inria
OPIS team. He is the co-author of 6 books and over 200 articles in the area of mathematical morphology, discrete
geometry, combinatorial and continuous optimization.
\end{document}

>>>>

\paragraph{Hugues Talbot}
Hugues Talbot received the Habilitation from Universite Paris-Est in
2013, the PhD from \'Ecole des Mines de Paris in 1993 and the
engineering degree from Ecole Centrale de Paris in 1989. He was
principal research scientist at CSIRO, Sydney, from 1994 to 2004; and
a professor in computer science at ESIEE Paris from 2004 to 2018. He
is now a professor in the mathematics department at CentraleSupelec,
Universite Paris-Saclay and member of the Inria OPIS team. He is the
co-author or co-editor of 7 books and over 250 articles in the area of
mathematical morphology, discrete geometry, combinatorial and
continuous optimization.
\end{document}
